%% ============================================================
%%  sections/experience.tex  —  Professional Experience
%%
%%  Sections:
%%    1. Professional Experience (4 main roles)
%%    2. Additional Experience   (condensed earlier roles)
%%    3. Career Highlights
%%
%%  REVIEW NOTES:
%%    - IDM / Scotiabank: content provided verbatim by candidate.
%%    - DaCodes, Outcoding, Globant: marked with %% REVIEW — replace
%%      with exact bullets from your current CV if different.
%% ============================================================

\section{Professional Experience}

%% ── 1. IDM Technology / Scotiabank  (March 2026 – Present) ──
\cvEntryClient%
  {Senior Fullstack Developer}%
  {IDM Technology}%
  {Scotiabank Peru}%
  {Dynamic QR Payments Platform}%
  {March 2026 -- Present \enspace\textbar\enspace 6-month contract}

\begin{cvItems}
  \cvItem{Developed cloud-native reactive microservices using \textbf{Java 25, Spring Boot 4} and
    \textbf{Spring WebFlux} for a dynamic QR payments platform.}
  \cvItem{Designed and implemented microservices supporting \textbf{dynamic and static QR generation}
    for interoperable digital wallet payments.}
  \cvItem{Built \textbf{REST APIs} for QR management, payment processing, and transaction persistence.}
  \cvItem{Developed \textbf{integration microservices} connecting Google Cloud services with IBM AS/400
    mainframe systems through DataQueues.}
  \cvItem{Implemented authentication and authorization mechanisms following \textbf{banking security
    standards} (Spring Security).}
  \cvItem{Designed persistence layers using \textbf{Microsoft SQL Server}; applied query optimization
    for high-throughput transactional workloads.}
  \cvItem{Worked with \textbf{Google Cloud Platform (GCP)} and \textbf{Apigee} for secure,
    policy-driven API management.}
  \cvItem{Participated in \textbf{Jenkins CI/CD} pipelines and maintained code quality with
    \textbf{SonarCloud}; resolved vulnerabilities identified during penetration testing.}
  \cvItem{Collaborated in cross-functional Agile Scrum teams using Jira, Confluence, and Bitbucket.}
\end{cvItems}

{\footnotesize\color{cvMuted}\textit{Stack:}~%
Java 25, Spring Boot 4, Spring WebFlux, Reactive Programming, REST APIs, SQL Server,
IBM AS/400, DataQueues, Spring Security, GCP, Apigee, Jenkins, SonarCloud, Bitbucket.}

\vspace{4pt}

%% ── 2. DaCodes — AgentCloud  (January 2025 – Present) ───────
%%  REVIEW: Replace bullets with exact content from your current CV.
\cvEntryClient%
  {Lead Software Engineer}%
  {DaCodes}%
  {HealthCare}%
  {AgentCloud}%
  {January 2025 -- February 2026}

\begin{cvItems}
  \cvItem{Spearheaded architecture and full-stack development of \textbf{AgentCloud}, an enterprise
    AI agent orchestration platform serving clients across the United States.}
  \cvItem{Designed cloud-native microservices on \textbf{AWS} (Lambda, EKS, SQS) using Java and
    Spring Boot; containerized with Docker and deployed via Kubernetes.}
  \cvItem{Built \textbf{React} frontend enabling real-time configuration, monitoring, and deployment
    of AI agent workflows for non-technical business users.}
  \cvItem{Defined engineering standards, performed code reviews, and led a distributed team of
    engineers through daily Agile ceremonies.}
  \cvItem{Implemented \textbf{CI/CD pipelines} (GitHub Actions) and \textbf{event-driven} backend
    services using Apache Kafka for real-time agent coordination.}
\end{cvItems}

\vspace{4pt}

%% ── 3. ExSquared (formerly Outcoding) / SambaSafety — Qorta  (March 2023 – Dec 2024)
%%  REVIEW: Replace bullets with exact content from your current CV.
\cvEntryClient%
  {Senior Full Stack Engineer}%
  {ExSquared}%
  {SambaSafety}%
  {Qorta}%
  {March 2023 -- December 2024}

\begin{cvItems}
  \cvItem{Contributed to \textbf{Qorta}, SambaSafety's driver risk monitoring and analytics platform
    used by fleet operators across North America.}
  \cvItem{Built scalable \textbf{REST APIs} using \textbf{NestJS / Node.js} and integrated with motor
    vehicle record (MVR) data providers across 50+ U.S. jurisdictions.}
  \cvItem{Developed \textbf{Angular} dashboard components for risk score visualization, driver
    compliance reporting, and real-time alert management.}
  \cvItem{Implemented data processing workflows using \textbf{Kafka} and \textbf{Redis}; optimized
    \textbf{PostgreSQL} queries for large-scale driver record datasets.}
  \cvItem{Maintained 85\%+ test coverage using \textbf{Jest} and \textbf{Karma}; collaborated
    in Agile Scrum teams with distributed U.S.-based engineers.}
\end{cvItems}

\vspace{4pt}

%% ── 4. Globant / Banco GNB Paraguay  (June 2022 – May 2023) ──
%%  REVIEW: Replace bullets with exact content from your current CV.
\cvEntryClient%
  {Senior Full Stack Engineer}%
  {Globant}%
  {Banco GNB Paraguay}%
  {Digital Banking Platform}%
  {June 2022 -- May 2023}

\begin{cvItems}
  \cvItem{Delivered digital banking features as a Globant-embedded engineer within Banco GNB
    Paraguay's core product team.}
  \cvItem{Developed \textbf{Java / Spring Boot} microservices for account management, transaction
    processing, and customer onboarding.}
  \cvItem{Built \textbf{Angular} modules for the bank's online portal; integrated with core banking
    systems through \textbf{REST APIs} and messaging layers.}
  \cvItem{Applied security-focused development practices to meet financial regulatory compliance in
    the Paraguayan banking sector.}
\end{cvItems}

%% ── Additional Experience (condensed) ────────────────────────
\section{Additional Experience}

{\small
\cvMiniEntry{Full Stack Engineer}{The Bridge Social (Remote, USA)}
\cvMiniEntry{Full Stack Engineer}{INDRA\enspace\textbar\enspace Clients: BCP, RIMAC}
\cvMiniEntry{Full Stack Engineer}{Michael Page\enspace\textbar\enspace Client: Intercorp}
\cvMiniEntry{Full Stack Engineer}{Zoluxiones\enspace\textbar\enspace Client: SURA}
\cvMiniEntry{Full Stack Engineer}{Experis\enspace\textbar\enspace Client: Equifax}
\cvMiniEntry{Full Stack Engineer}{Olva Courier}
\cvMiniEntry{Full Stack Engineer}{LimaW}
}

%% ── Career Highlights ─────────────────────────────────────────
\section{Career Highlights}

\begin{cvItems}
  \cvItem{\textbf{12+ years} of professional software engineering across Healthcare, Banking,
    Insurance, Retail, and Logistics industries.}
  \cvItem{Delivered production solutions for blue-chip clients: \textbf{Scotiabank}, SambaSafety,
    Banco GNB Paraguay, Equifax, Intercorp, SURA, RIMAC, and BCP.}
  \cvItem{Led distributed engineering teams on remote-first projects across the \textbf{United States,
    Latin America, and the Caribbean}.}
  \cvItem{Proven expertise in \textbf{modernizing legacy banking and insurance systems} to
    cloud-native microservices architectures.}
  \cvItem{Consistently delivered in regulated, high-availability environments with strict
    security and compliance requirements.}
\end{cvItems}
